---
title: "RSI Exercise"
author: "Rohan Agarwal"
date: '2022-10-14'
output:
  html_document: default
  pdf_document: default
---

```{r setup}
library (haven)
library (Hmisc)
library (stargazer)
library (tidyverse)
library (dplyr)
library(ggplot2)
library (TSstudio)
library (zoo)
library(data.table)
setwd("~/Desktop/HFT/Trading indicators python/Trading-Indicators")

```

# In this R practice, I will use stock price data from the past 5 years to construct a Relative Stength Index. \n  
**The RSI is a momentum indicator that is used in technical analysis to:**  \n

- measure the speed and magnitude of a security's recent price changes.  \n

- evaluate undervalued and overvalued conditions in security price.  \n

The RSI indicates securities primed for trend reversals and collective price pullbacks. \n

It signals to traders when to buy and when to sell. \n

- **RSI > 70:** the stock is overbought **(overvalued).**  \n

- **RSI < 30:** the stock is oversold **(undervalued).**  \n 

It compares the strength of securities on days when prices go up to the strength on days when they go down. \n

$$
RSI_{stepone}= 100 - [\frac{100}{1+\frac{avg. gain}{avg. loss}}]
$$

$$
RSI_{steptwo} = 100 - [\frac{100}{1 + \frac{(Pvt. Avg. Gain * 13)+current gain}
{(Pvt. Avg. Loss * 13) + current loss}}]
$$
**Installing the libraries that will allow me to download the data.**  \n

For this program, I will calculate the RSI for the following 6 tech stocks:  \n
- Meta  \n

- Amazon  \n

- Apple  \n

- Netflix \n

- Google  \n

- Microsoft  \n

```{r libraries to download the data from Yahoo finance}
library(quantmod)
library (broom)
library (magrittr)
```

Defining the start and end dates for the program and getting the stock price data required. \n

```{r dates}
start <- as.Date ("2017-10-14")
end <- as.Date ("2022-10-14")
getSymbols(c("META", "AMZN","AAPL","NFLX","GOOG","MSFT"), src = "yahoo", from = start, to = end)
```

## Reorganizing the data to keep only the adjusted closing share price \n
**Using an XTS object for the share price time series data.** \n

```{r}
stocks = as.xts(data.frame (Meta = META[,"META.Adjusted"],
                            Amazon = AMZN[, "AMZN.Adjusted"],
                            Apple = AAPL[, "AAPL.Adjusted"],
                            Netflix = NFLX[, "NFLX.Adjusted"],
                            Alphabet = GOOG[, "GOOG.Adjusted"],
                            Microsoft = MSFT[, "MSFT.Adjusted"])
                )
colnames(stocks) <- c("Meta", "Amazon", "Apple", "Netflix", "Alphabet", "Microsoft")
index(stocks) = as.Date(index(stocks))
```


**Plotting the stock prices of the 6 stocks of interest.** \n

```{r}
stocks_series = tidy(stocks) %>%
  ggplot(aes(x= index, y = value, color = series))+
  labs(title = "Stock prices of 6 large US technology companies",
       subtitle = "Dates: October 14, 2017 to October 14, 2022",
       caption = "Source: Yahoo Finance")+
  xlab("Date") + ylab ("Price (US$)") + 
  scale_color_manual(values = c("Blue", "Yellow", "Gray", "Red", "Green", "Orange")) +
  geom_line()

stocks_series
```

# Programming the RSI function.  \n

- First, I will program RSI functions for each of the six stocks which I have. \n

- Step 1 : add columns containing the RSI for each of the six stocks next to their adjusted closing price. \n

- Step 2: Create diagrams with the stock price graph above and the RSI graph below for each of the six stocks chosen for this analysis. 


```{r}


myRSI <- function (price,n){
  N <- length(price)
  U <- rep(0,N)
  D <- rep(0,N)
  rsi <- rep(NA,N)
  Lprice <- Lag(price,1)
  for (i in 2:N){
    if (price[i]>=Lprice[i]){
      U[i] <- 1
    } else {
      D[i] <- 1
    }
    if (i>n){
      AvgUp <- mean(U[(i-n+1):i])
      AvgDn <- mean(D[(i-n+1):i])
      rsi[i] <- AvgUp/(AvgUp+AvgDn)*100 
      }
    }
  rsi <- reclass(rsi, price)
  return(rsi)
}


rsi_meta <- myRSI(stocks$Meta, n = 14)
rsi_amzn <-myRSI(stocks$Amazon, n =14)
rsi_aapl <- myRSI(stocks$Apple, n = 14)
rsi_nflx <- myRSI (stocks$Netflix, n = 14)
rsi_goog <- myRSI (stocks$Alphabet, n =14)
rsi_msft <- myRSI (stocks$Microsoft, n = 14)

```

**Adding the 6 RSI XTS objects to the stocks XTS object and dsiplaying descriptive statistics about the RSIs**

``` {r}
stocks.f <- merge (stocks, rsi_meta, rsi_amzn, rsi_aapl, rsi_nflx, rsi_goog, rsi_msft)
colnames(stocks.f) <- c("Meta", "Amazon", "Apple", "Netflix", "Alphabet", "Microsoft", "Meta RSI", "Amazon RSI", 
                        "Apple RSI", "Netflix RSI", "Alphabet RSI", "Microsoft RSI")
stocks.df <- as.data.frame(stocks.f)

stargazer (stocks.df, min.max = TRUE, mean.sd = TRUE, nobs = TRUE, median = TRUE, 
           iqr = TRUE, align = TRUE,
           type = "text", title = "Descriptive Statistics about the mean stock price and RSI functions of the six technology companies", 
           digits = 3)
```

**Creating graphs using *ggplot2* with the stock price on top and the RSI on the bottom **

```{r}

stocks_series2 = tidy(stocks.f) %>% 
  
  ggplot(aes(x=index,y=value, color=series)) + 
  geom_line() +
  facet_grid(series~.,scales = "free") + 
  labs(title = "6 Large US Technology Companies October 14, 2017 to October 14, 2022",
                                              
                                              subtitle = "End of Day Adjusted Prices and RSI",
                                              caption = " Source: Yahoo Finance") +
  
  xlab("Date") + ylab("Price($) and RSI (0 to 100)") +
  scale_color_manual(values = c("Red", "Black", "DarkBlue","Orange", "Grey", "Pink", "Brown", "Yellow", "Green", "Blue", "Purple", "Blue"))
stocks_series2

```



